---
title: "Homework_4"
author: "Ben Rodwell"
date: "April 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load the data
d <- read.csv("KamilarAndCooperData.csv", header = T, sep = ",")
head(d)
str(d)
```



# [1]
## Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).
```{r}
model <- lm(data = d, formula = log(HomeRange_km2) ~ log(Body_mass_female_mean))
model
summary(model)
par(mfrow = c(2,2))

# Coefficients
model$coefficients
```






# [2]
## Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the appropriate coefficients. This generates a sampling distribution for each β coefficient. Plot a histogram of these sampling distributions.

```{r}
n <- length(d[,1]) # Number of observations
dsample <- d[sample(nrow(d), n, replace = T), ]
head(dsample)
str(dsample)

## Loop to repeat it 1000 times while storing the beta coefficients
n <- length(d[,1]) # Number of observations/rows in the dataset
b <- 1000
beta0 <- rep(0,b) # empty vector for bootstrapped beta0 values
beta1 <- rep(0,b) # empty vector for bootstrapped beta1 values
for (i in 1:b){
  dsample <- d[sample(nrow(d), n, replace = T), ]
  model <- lm(data = dsample, formula = log(HomeRange_km2) ~ log(Body_mass_female_mean))
  beta0[i] <- model$coefficients[1] # storing the beta0 value in the empty vector
  beta1[i] <- model$coefficients[2] # storing the beta1 value in the empty vector
  }
head(beta1)
head(beta0)

## Histograms of the bootstrapped beta distributions
par(mfrow = c(1,2))
hist(beta0)
hist(beta1)
par(mfrow = c(1,1))
```



# [3]
## Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap.

```{r}
SEbeta0 <- sd(beta0)
SEbeta0
SEbeta1 <- sd(beta1)
SEbeta1
```


# [4]
## Also determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

```{r}

```


# [5]
## How does your answer to part [3] compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

```{r}

```


# [6]
## How does your answer to part [4] compare to the 95% CI estimated from your entire dataset?

```{r}

```

